Reproductive Allocation Calculations

### 2014-12-22 CarbonInvestments.Rnw
User maker and knitr to generate plot and document

\clearpage
\newpage
\section{BAER}
\begin{multicols}{2}
\includegraphics[width=3in]{images/BAER.png}
\vfill
\columnbreak
\input{tables/BAER.tex}
\end{multicols}

\clearpage
\newpage
\section{BOLE}
\begin{multicols}{2}
\includegraphics[width=3in]{images/BOLE.png}
\vfill
\columnbreak
\input{tables/BOLE.tex}
\end{multicols}

@@

\section{COER}
\begin{multicols}{2}
\includegraphics[width=2.7in]{images/COER.png}
\vfill
\columnbreak
\input{tables/COER.tex}
\end{multicols}

@@

\section{EPMI}
\begin{multicols}{2}
\includegraphics[width=2.5in]{images/EPMI.png}
\vfill
\columnbreak
\input{tables/EPMI.tex}
\end{multicols}

@@

\section{GRBU}
\begin{multicols}{2}
\includegraphics[width=3in]{images/GRBU.png}
\vfill
\columnbreak

\input{tables/GRBU.tex}\\

\end{multicols}

@@

\section{GRSP}
\begin{multicols}{2}
\includegraphics[width=3in]{images/GRSP.png}
\vfill
\columnbreak

\input{tables/GRSP.tex}

\end{multicols}

\clearpage
\newpage
\section{HATE}
\begin{multicols}{2}
\includegraphics[width=3in]{images/HATE.png}
\vfill
\columnbreak
\input{tables/HATE.tex}

\end{multicols}

@@

\section{HEPU}
\begin{multicols}{2}
\includegraphics[width=3in]{images/HEPU.png}
\vfill
\columnbreak
\input{tables/HEPU.tex}
\end{multicols}

@@

\section{LEES}
\begin{multicols}{2}
\includegraphics[width=3in]{images/LEES.png}
\vfill
\columnbreak
%%%%
\input{tables/LEES.tex}
%%%%%
\\
\end{multicols}
\clearpage
\newpage

\section{PELA}
\begin{multicols}{2}
\includegraphics[width=2.8in]{images/PELA.png}
\vfill
\columnbreak
\input{tables/PELA.tex}
\end{multicols}

\clearpage
\newpage
\section{PEPU}
\begin{multicols}{2}
\includegraphics[width=2.7in]{images/PEPU.png}
\vfill
\columnbreak
\input{tables/PEPU.tex}
\end{multicols}
\clearpage
\newpage

\clearpage
\newpage
\section{PHPH}
\begin{multicols}{2}
\includegraphics[width=3in]{images/PHPH.png}
\vfill
\columnbreak
\input{tables/PHPH.tex}
\end{multicols}

\clearpage
\newpage
\section{PILI}
\begin{multicols}{2}
\includegraphics[width=2.7in]{images/PILI.png}
\vfill
\columnbreak
\input{tables/PILI.tex}
\end{multicols}

\clearpage
\newpage
\section{PUTU}
\begin{multicols}{2}
\includegraphics[width=2.5in]{images/PUTU.png}
\vfill
\columnbreak
\input{tables/PUTU.tex}
\end{multicols}

\chapter{Additional preliminary calculations}

\section{Average count/length values}

\begin{figure}[h!]
\begin{center}
\input{tables/AvCountsPerMM.tex}
\end{center}
\caption{Table summarising the average number of elements per mm. To be used for calculations of mass based on the length for conversion to counts.}
\end{figure}

% TODO: Include these plots
% \section{Regression Fits and Coefficients}
% \subsection*{GRBU}
% \begin{center}
% \includegraphics[width=2.7in]{figures/GRBU_fruit_large_immature.pdf}
% \includegraphics[width=2.7in]{figures/GRBU_seed_pod.pdf}
% \end{center}

% \subsection{GRSP}
% \begin{center}
% \includegraphics[width=2.7in]{figures/GRSP_fruit_large_immature.pdf}
% \includegraphics[width=2.7in]{figures/GRSP_seed_pod.pdf}
% \end{center}

% \subsection{PELA}
% \begin{center}
% \includegraphics[width=2.7in]{figures/PELA_fruit_large_immature.pdf}
% \includegraphics[width=2.7in]{figures/PELA_seed_pod.pdf}\\
% \includegraphics[width=2.7in]{figures/PELA_seed.pdf}
% \end{center}

% \subsection{BAER}
% \begin{center}
% \includegraphics[width=2.7in]{figures/BAER_cone_young.pdf}
% \includegraphics[width=2.7in]{figures/BAER_cone_green.pdf}\\
% \includegraphics[width=2.7in]{figures/BAER_cone_brown_no_expanded_follicles.pdf}
% \includegraphics[width=2.7in]{figures/BAER_cone_brown.pdf}\\
% \includegraphics[width=2.7in]{figures/BAER_cone_aborted.pdf}
% \includegraphics[width=2.7in]{figures/BAER_cone_base_green.pdf}\\
% \includegraphics[width=2.7in]{figures/BAER_cone_base_brown.pdf}
% \end{center}

% \subsection{PEPU}
% \begin{center}
% \includegraphics[width=2.7in]{figures/PEPU_cone_green.pdf}
% \includegraphics[width=2.7in]{figures/PEPU_cone_brown.pdf}\\
% \includegraphics[width=2.7in]{figures/PEPU_cone_aborted.pdf}
% \end{center}

\newpage
\subsection{Summary table for regression}
\begin{figure}[h!]
\begin{center}
\input{tables/RegressionTable.tex}
\end{center}
\caption{Table summarising the equations used to determine weights of individual plant parts by using their size.}
\end{figure}

\chapter{Preliminary results}
\section{Reproductive allocation results}
\subsection{Overview}
\includegraphics[width=1\linewidth]{figures/RA_comparison_age.pdf}
\includegraphics[width=1\linewidth]{figures/RA_comparison_diam.pdf}
\includegraphics[width=1\linewidth]{figures/RA_comparison_weight.pdf}
\clearpage

TODO:Add this material back in

\newpage
\section{Individual species}
\subsection{BAER}
\includegraphics[width=1\linewidth]{figures/RA_age_BAER.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_BAER.pdf}

\clearpage
\newpage
\subsection{BOLE}
\includegraphics[width=1\linewidth]{figures/RA_age_BOLE.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_BOLE.pdf}

\clearpage
\newpage
\subsection{COER}
\includegraphics[width=1\linewidth]{figures/RA_age_COER.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_COER.pdf}

\clearpage
\newpage
\subsection{EPMI}
\includegraphics[width=1\linewidth]{figures/RA_age_EPMI.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_EPMI.pdf}

\clearpage
\newpage
\subsection{GRBU}
\includegraphics[width=1\linewidth]{figures/RA_age_GRBU.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_GRBU.pdf}

\clearpage
\newpage
\subsection{GRSP}
\includegraphics[width=1\linewidth]{figures/RA_age_GRSP.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_GRSP.pdf}

\clearpage
\newpage
\subsection{HATE}
\includegraphics[width=1\linewidth]{figures/RA_age_HATE.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_HATE.pdf}

\clearpage
\newpage
\subsection{HEPU}
\includegraphics[width=1\linewidth]{figures/RA_age_HEPU.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_HEPU.pdf}

\clearpage
\newpage
\subsection{LEES}
\includegraphics[width=1\linewidth]{figures/RA_age_LEES.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_LEES.pdf}

\clearpage
\newpage
\subsection{PELA}
\includegraphics[width=1\linewidth]{figures/RA_age_PELA.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PELA.pdf}

\clearpage
\newpage
\subsection{PEPU}
\includegraphics[width=1\linewidth]{figures/RA_age_PEPU.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PEPU.pdf}

\clearpage
\newpage
\subsection{PHPH}
\includegraphics[width=1\linewidth]{figures/RA_age_PHPH.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PHPH.pdf}

\clearpage
\newpage
\subsection{PILI}
\includegraphics[width=1\linewidth]{figures/RA_age_PILI.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PILI.pdf}

\clearpage
\newpage
\subsection{PUTU}
\includegraphics[width=1\linewidth]{figures/RA_age_PUTU.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PUTU.pdf}

% \newpage
% \section{Investment in Accessory Tissues}
% \subsection{Overview}
% \includegraphics[width=1\linewidth]{figures/IAT_Comparison.pdf}
% \clearpage
% \newpage
% \section{Individual species}
% \subsection{BAER}
% \includegraphics[width=1\linewidth]{figures/IAT_BAER.pdf}

% \subsection{BOLE}
% \includegraphics[width=1\linewidth]{figures/IAT_BOLE.pdf}

% \subsection{COER}
% \includegraphics[width=1\linewidth]{figures/IAT_COER.pdf}

% \subsection{EPMI}
% \includegraphics[width=1\linewidth]{figures/IAT_EPMI.pdf}

% \subsection{GRBU}
% \includegraphics[width=1\linewidth]{figures/IAT_GRBU.pdf}

% \subsection{GRSP}
% \includegraphics[width=1\linewidth]{figures/IAT_GRSP.pdf}

% \subsection{HATE}
% \includegraphics[width=1\linewidth]{figures/IAT_HATE.pdf}

% \subsection{HEPU}
% \includegraphics[width=1\linewidth]{figures/IAT_HEPU.pdf}

% \subsection{LEES}
% \includegraphics[width=1\linewidth]{figures/IAT_LEES.pdf}

% \subsection{PELA}
% \includegraphics[width=1\linewidth]{figures/IAT_PELA.pdf}

% \subsection{PEPU}
% \includegraphics[width=1\linewidth]{figures/IAT_PEPU.pdf}

% \subsection{PHPH}
% \includegraphics[width=1\linewidth]{figures/IAT_PHPH.pdf}

% \subsection{PILI}
% \includegraphics[width=1\linewidth]{figures/IAT_PILI.pdf}

% \subsection{PUTU}
% \includegraphics[width=1\linewidth]{figures/IAT_PUTU.pdf}

>>>>

<<tablepreload1, echo=FALSE>>=
print_table <- function(x, caption, label=NULL){
  if(!is.null(x) && nrow(x) > 0)
 	  print(xtable(x,caption=caption, label=label,  type="latex"),
               include.rownames=FALSE, hline.after=c(0,nrow(x)), caption.placement="top")
}
@

@@

\section{BAER}

\includegraphics[height=6in]{images/BAER.png}
<<results='asis', echo=FALSE>>=
 print_table(BAER_PartsSummary$AvWeightPerUnit,
 caption="BAER: Average weight of parts")
@

<<results='asis', echo=FALSE>>=
 print_table(BAER_PartsSummary$AvCountsPerMM,
 caption="BAER: Average density of parts for per mm")
@

<<results='asis', echo=FALSE>>=
 print_table(BAER_PartsSummary$RegressionTable,
 caption="BAER: Coefficients of regressions used to estimate weights for some parts")
@

@@

\section{BOLE}

\includegraphics[height=6in]{images/BOLE.png}
<<results='asis', echo=FALSE>>=
 print_table(BOLE_PartsSummary$AvWeightPerUnit,
 caption="BOLE: Average weight of parts")

 print_table(BOLE_PartsSummary$AvCountsPerMM,
 caption="BOLE: Average density of parts for per mm")

 print_table(BOLE_PartsSummary$RegressionTable,
 caption="BOLE: Coefficients of regressions used to estimate weights for some parts")
@

@@

\section{COER}

\includegraphics[height=6in]{images/COER.png}
<<results='asis', echo=FALSE>>=
 print_table(COER_PartsSummary$AvWeightPerUnit,
 caption="COER: Average weight of parts")

 print_table(COER_PartsSummary$AvCountsPerMM,
 caption="COER: Average density of parts for per mm")

 print_table(COER_PartsSummary$RegressionTable,
 caption="COER: Coefficients of regressions used to estimate weights for some parts")
@

@@

\section{EPMI}

\includegraphics[height=6in]{images/EPMI.png}
<<results='asis', echo=FALSE>>=
 print_table(EPMI_PartsSummary$AvWeightPerUnit,
 caption="EPMI: Average weight of parts")

<<results='asis', echo=FALSE>>=
 print_table(EPMI_PartsSummary$AvCountsPerMM,
 caption="EPMI: Average density of parts for per mm")

<<results='asis', echo=FALSE>>=
 print_table(EPMI_PartsSummary$RegressionTable,
 caption="EPMI: Coefficients of regressions used to estimate weights for some parts")
@

@@

\section{GRBU}

\includegraphics[height=6in]{images/GRBU.png}
<<results='asis', echo=FALSE>>=
 print_table(GRBU_PartsSummary$AvWeightPerUnit,
 caption="GRBU: Average weight of parts")

<<results='asis', echo=FALSE>>=
 print_table(GRBU_PartsSummary$AvCountsPerMM,
 caption="GRBU: Average density of parts for per mm")

<<results='asis', echo=FALSE>>=
 print_table(GRBU_PartsSummary$RegressionTable,
 caption="GRBU: Coefficients of regressions used to estimate weights for some parts")
@

@@

\section{GRSP}

\includegraphics[height=6in]{images/GRSP.png}
<<results='asis', echo=FALSE>>=
 print_table(GRSP_PartsSummary$AvWeightPerUnit,
 caption="GRSP: Average weight of parts")

<<results='asis', echo=FALSE>>=
 print_table(GRSP_PartsSummary$AvCountsPerMM,
 caption="GRSP: Average density of parts for per mm")

<<results='asis', echo=FALSE>>=
 print_table(GRSP_PartsSummary$RegressionTable,
 caption="GRSP: Coefficients of regressions used to estimate weights for some parts")
@

\section{HATE}

\includegraphics[height=6in]{images/HATE.png}
<<results='asis', echo=FALSE>>=
 print_table(HATE_PartsSummary$AvWeightPerUnit,
 caption="HATE: Average weight of parts")

<<results='asis', echo=FALSE>>=
 print_table(HATE_PartsSummary$AvCountsPerMM,
 caption="HATE: Average density of parts for per mm")

<<results='asis', echo=FALSE>>=
 print_table(HATE_PartsSummary$RegressionTable,
 caption="HATE: Coefficients of regressions used to estimate weights for some parts")
@

\section{HEPU}

\includegraphics[height=6in]{images/HEPU.png}
<<results='asis', echo=FALSE>>=
 print_table(HEPU_PartsSummary$AvWeightPerUnit,
 caption="HEPU: Average weight of parts")

<<results='asis', echo=FALSE>>=
 print_table(HEPU_PartsSummary$AvCountsPerMM,
 caption="HEPU: Average density of parts for per mm")

<<results='asis', echo=FALSE>>=
 print_table(HEPU_PartsSummary$RegressionTable,
 caption="HEPU: Coefficients of regressions used to estimate weights for some parts")
@

\section{LEES}

\includegraphics[height=6in]{images/LEES.png}
<<results='asis', echo=FALSE>>=
 print_table(LEES_PartsSummary$AvWeightPerUnit,
 caption="LEES: Average weight of parts")

<<results='asis', echo=FALSE>>=
 print_table(LEES_PartsSummary$AvCountsPerMM,
 caption="LEES: Average density of parts for per mm")

<<results='asis', echo=FALSE>>=
 print_table(LEES_PartsSummary$RegressionTable,
 caption="LEES: Coefficients of regressions used to estimate weights for some parts")
@

\section{PELA}

\includegraphics[height=6in]{images/PELA.png}
<<results='asis', echo=FALSE>>=
 print_table(PELA_PartsSummary$AvWeightPerUnit,
 caption="PELA: Average weight of parts")

<<results='asis', echo=FALSE>>=
 print_table(PELA_PartsSummary$AvCountsPerMM,
 caption="PELA: Average density of parts for per mm")

<<results='asis', echo=FALSE>>=
 print_table(PELA_PartsSummary$RegressionTable,
 caption="PELA: Coefficients of regressions used to estimate weights for some parts")
@

\section{PEPU}

\includegraphics[height=6in]{images/PEPU.png}
<<results='asis', echo=FALSE>>=
 print_table(PEPU_PartsSummary$AvWeightPerUnit,
 caption="PEPU: Average weight of parts")

<<results='asis', echo=FALSE>>=
 print_table(PEPU_PartsSummary$AvCountsPerMM,
 caption="PEPU: Average density of parts for per mm")

<<results='asis', echo=FALSE>>=
 print_table(PEPU_PartsSummary$RegressionTable,
 caption="PEPU: Coefficients of regressions used to estimate weights for some parts")
@

\section{PHPH}

\includegraphics[height=6in]{images/PHPH.png}
<<results='asis', echo=FALSE>>=
 print_table(PHPH_PartsSummary$AvWeightPerUnit,
 caption="PHPH: Average weight of parts")

<<results='asis', echo=FALSE>>=
 print_table(PHPH_PartsSummary$AvCountsPerMM,
 caption="PHPH: Average density of parts for per mm")

<<results='asis', echo=FALSE>>=
 print_table(PHPH_PartsSummary$RegressionTable,
 caption="PHPH: Coefficients of regressions used to estimate weights for some parts")
@

\section{PILI}

\includegraphics[height=6in]{images/PILI.png}
<<results='asis', echo=FALSE>>=
 print_table(PILI_PartsSummary$AvWeightPerUnit,
 caption="PILI: Average weight of parts")

<<results='asis', echo=FALSE>>=
 print_table(PILI_PartsSummary$AvCountsPerMM,
 caption="PILI: Average density of parts for per mm")

<<results='asis', echo=FALSE>>=
 print_table(PILI_PartsSummary$RegressionTable,
 caption="PILI: Coefficients of regressions used to estimate weights for some parts")
@

\section{PUTU}

\includegraphics[height=6in]{images/PUTU.png}
<<results='asis', echo=FALSE>>=
 print_table(PUTU_PartsSummary$AvWeightPerUnit,
 caption="PUTU: Average weight of parts")

<<results='asis', echo=FALSE>>=
 print_table(PUTU_PartsSummary$AvCountsPerMM,
 caption="PUTU: Average density of parts for per mm")

<<results='asis', echo=FALSE>>=
 print_table(PUTU_PartsSummary$RegressionTable,
 caption="PUTU: Coefficients of regressions used to estimate weights for some parts")
@

% \chapter{Additional preliminary calculations}

% TODO: Include these plots
% \section{Regression Fits and Coefficients}
% \subsection*{GRBU}
% \begin{center}
% \includegraphics[width=2.7in]{figure/GRBU_fruit_large_immature.pdf}
% \includegraphics[width=2.7in]{figure/GRBU_seed_pod.pdf}
% \end{center}

% \subsection{GRSP}
% \begin{center}
% \includegraphics[width=2.7in]{figure/GRSP_fruit_large_immature.pdf}
% \includegraphics[width=2.7in]{figure/GRSP_seed_pod.pdf}
% \end{center}

% \subsection{PELA}
% \begin{center}
% \includegraphics[width=2.7in]{figure/PELA_fruit_large_immature.pdf}
% \includegraphics[width=2.7in]{figure/PELA_seed_pod.pdf}\\
% \includegraphics[width=2.7in]{figure/PELA_seed.pdf}
% \end{center}

% \subsection{BAER}
% \begin{center}
% \includegraphics[width=2.7in]{figure/BAER_cone_young.pdf}
% \includegraphics[width=2.7in]{figure/BAER_cone_green.pdf}\\
% \includegraphics[width=2.7in]{figure/BAER_cone_brown_no_expanded_follicles.pdf}
% \includegraphics[width=2.7in]{figure/BAER_cone_brown.pdf}\\
% \includegraphics[width=2.7in]{figure/BAER_cone_aborted.pdf}
% \includegraphics[width=2.7in]{figure/BAER_cone_base_green.pdf}\\
% \includegraphics[width=2.7in]{figure/BAER_cone_base_brown.pdf}
% \end{center}

% \subsection{PEPU}
% \begin{center}
% \includegraphics[width=2.7in]{figure/PEPU_cone_green.pdf}
% \includegraphics[width=2.7in]{figure/PEPU_cone_brown.pdf}\\
% \includegraphics[width=2.7in]{figure/PEPU_cone_aborted.pdf}
% \end{center}

% \newpage
% \subsection{Summary table for regression}
% \begin{figure}[h!]
% \begin{center}
% \input{tables/RegressionTable.tex}
% \end{center}
% \caption{Table summarising the equations used to determine weights of individual plant parts by using their size.}
% \end{figure}

% \chapter{Preliminary results}
% \section{Reproductive allocation results}
% \subsection{Overview}
% \includegraphics[width=1\linewidth]{figure/RA_comparison_age.pdf}
% \includegraphics[width=1\linewidth]{figure/RA_comparison_diam.pdf}
% \includegraphics[width=1\linewidth]{figure/RA_comparison_weight.pdf}
% \clearpage
 \clearpage
 \newpage

 \subsection{ BAER }

<<results='asis', echo=FALSE>>=
	plot_species_ReproductionAllocation_age_panel(BAER_ReproductionAllocation)
	plot_species_ReproductionAllocation_weight_diam_panel(BAER_ReproductionAllocation)
@

 \subsection{ BOLE }

<<results='asis', echo=FALSE>>=
	plot_species_ReproductionAllocation_age_panel(BOLE_ReproductionAllocation)
	plot_species_ReproductionAllocation_weight_diam_panel(BOLE_ReproductionAllocation)
@

 \subsection{ COER }

<<results='asis', echo=FALSE>>=
	plot_species_ReproductionAllocation_age_panel(COER_ReproductionAllocation)
	plot_species_ReproductionAllocation_weight_diam_panel(COER_ReproductionAllocation)
@

 \subsection{ EPMI }

<<results='asis', echo=FALSE>>=
	plot_species_ReproductionAllocation_age_panel(EPMI_ReproductionAllocation)
	plot_species_ReproductionAllocation_weight_diam_panel(EPMI_ReproductionAllocation)
@

 \subsection{ GRBU }

<<results='asis', echo=FALSE>>=
	plot_species_ReproductionAllocation_age_panel(GRBU_ReproductionAllocation)
	plot_species_ReproductionAllocation_weight_diam_panel(GRBU_ReproductionAllocation)
@

 \subsection{ GRSP }

<<results='asis', echo=FALSE>>=
	plot_species_ReproductionAllocation_age_panel(GRSP_ReproductionAllocation)
	plot_species_ReproductionAllocation_weight_diam_panel(GRSP_ReproductionAllocation)
@

 \subsection{ HATE }

<<results='asis', echo=FALSE>>=
	plot_species_ReproductionAllocation_age_panel(HATE_ReproductionAllocation)
	plot_species_ReproductionAllocation_weight_diam_panel(HATE_ReproductionAllocation)
@

 \subsection{ HEPU }

<<results='asis', echo=FALSE>>=
	plot_species_ReproductionAllocation_age_panel(HEPU_ReproductionAllocation)
	plot_species_ReproductionAllocation_weight_diam_panel(HEPU_ReproductionAllocation)
@

 \subsection{ LEES }

<<results='asis', echo=FALSE>>=
	plot_species_ReproductionAllocation_age_panel(LEES_ReproductionAllocation)
	plot_species_ReproductionAllocation_weight_diam_panel(LEES_ReproductionAllocation)
@

 \subsection{ PELA }

<<results='asis', echo=FALSE>>=
	plot_species_ReproductionAllocation_age_panel(PELA_ReproductionAllocation)
	plot_species_ReproductionAllocation_weight_diam_panel(PELA_ReproductionAllocation)
@

 \subsection{ PEPU }

<<results='asis', echo=FALSE>>=
	plot_species_ReproductionAllocation_age_panel(PEPU_ReproductionAllocation)
	plot_species_ReproductionAllocation_weight_diam_panel(PEPU_ReproductionAllocation)
@

 \subsection{ PHPH }

<<results='asis', echo=FALSE>>=
	plot_species_ReproductionAllocation_age_panel(PHPH_ReproductionAllocation)
	plot_species_ReproductionAllocation_weight_diam_panel(PHPH_ReproductionAllocation)
@

 \subsection{ PILI }

<<results='asis', echo=FALSE>>=
	plot_species_ReproductionAllocation_age_panel(PILI_ReproductionAllocation)
	plot_species_ReproductionAllocation_weight_diam_panel(PILI_ReproductionAllocation)
@

 \subsection{ PUTU }

<<results='asis', echo=FALSE>>=
	plot_species_ReproductionAllocation_age_panel(PUTU_ReproductionAllocation)
	plot_species_ReproductionAllocation_weight_diam_panel(PUTU_ReproductionAllocation)
@

% \clearpage
% \newpage
% \subsection{BOLE}
% \includegraphics[width=1\linewidth]{figure/RA_age_BOLE.pdf}
% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_BOLE.pdf}

% \clearpage
% \newpage
% \subsection{COER}
% \includegraphics[width=1\linewidth]{figure/RA_age_COER.pdf}
% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_COER.pdf}

% \clearpage
% \newpage
% \subsection{EPMI}
% \includegraphics[width=1\linewidth]{figure/RA_age_EPMI.pdf}
% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_EPMI.pdf}

% \clearpage
% \newpage
% \subsection{GRBU}
% \includegraphics[width=1\linewidth]{figure/RA_age_GRBU.pdf}
% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_GRBU.pdf}

% \clearpage
% \newpage
% \subsection{GRSP}
% \includegraphics[width=1\linewidth]{figure/RA_age_GRSP.pdf}
% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_GRSP.pdf}

% \clearpage
% \newpage
% \subsection{HATE}
% \includegraphics[width=1\linewidth]{figure/RA_age_HATE.pdf}
% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_HATE.pdf}

% \clearpage
% \newpage
% \subsection{HEPU}
% \includegraphics[width=1\linewidth]{figure/RA_age_HEPU.pdf}
% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_HEPU.pdf}

% \clearpage
% \newpage
% \subsection{LEES}
% \includegraphics[width=1\linewidth]{figure/RA_age_LEES.pdf}
% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_LEES.pdf}

% \clearpage
% \newpage
% \subsection{PELA}
% \includegraphics[width=1\linewidth]{figure/RA_age_PELA.pdf}
% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_PELA.pdf}

% \clearpage
% \newpage
% \subsection{PEPU}
% \includegraphics[width=1\linewidth]{figure/RA_age_PEPU.pdf}
% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_PEPU.pdf}

% \clearpage
% \newpage
% \subsection{PHPH}
% \includegraphics[width=1\linewidth]{figure/RA_age_PHPH.pdf}
% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_PHPH.pdf}

% \clearpage
% \newpage
% \subsection{PILI}
% \includegraphics[width=1\linewidth]{figure/RA_age_PILI.pdf}
% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_PILI.pdf}

% \clearpage
% \newpage
% \subsection{PUTU}
% \includegraphics[width=1\linewidth]{figure/RA_age_PUTU.pdf}
% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_PUTU.pdf}

% % \newpage
% % \section{Investment in Accessory Tissues}
% % \subsection{Overview}
% % \includegraphics[width=1\linewidth]{figure/IAT_Comparison.pdf}
% % \clearpage
% % \newpage
% % \section{Individual species}
% % \subsection{BAER}
% % \includegraphics[width=1\linewidth]{figure/IAT_BAER.pdf}

% % \subsection{BOLE}
% % \includegraphics[width=1\linewidth]{figure/IAT_BOLE.pdf}

% % \subsection{COER}
% % \includegraphics[width=1\linewidth]{figure/IAT_COER.pdf}

% % \subsection{EPMI}
% % \includegraphics[width=1\linewidth]{figure/IAT_EPMI.pdf}

% % \subsection{GRBU}
% % \includegraphics[width=1\linewidth]{figure/IAT_GRBU.pdf}

% % \subsection{GRSP}
% % \includegraphics[width=1\linewidth]{figure/IAT_GRSP.pdf}

% % \subsection{HATE}
% % \includegraphics[width=1\linewidth]{figure/IAT_HATE.pdf}

% % \subsection{HEPU}
% % \includegraphics[width=1\linewidth]{figure/IAT_HEPU.pdf}

% % \subsection{LEES}
% % \includegraphics[width=1\linewidth]{figure/IAT_LEES.pdf}

% % \subsection{PELA}
% % \includegraphics[width=1\linewidth]{figure/IAT_PELA.pdf}

% % \subsection{PEPU}
% % \includegraphics[width=1\linewidth]{figure/IAT_PEPU.pdf}

% % \subsection{PHPH}
% % \includegraphics[width=1\linewidth]{figure/IAT_PHPH.pdf}

% % \subsection{PILI}
% % \includegraphics[width=1\linewidth]{figure/IAT_PILI.pdf}

% % \subsection{PUTU}
% % \includegraphics[width=1\linewidth]{figure/IAT_PUTU.pdf}
